---
output:
  html_document: 
    theme: united
    toc: yes
    toc_depth: 4
  word_document:
    toc: yes
  pdf_document:
    highlight: zenburn
    toc: yes
always_allow_html: yes
---



#### 3-1 Table of FASTQC
FASTQC results are also spread to report file.
```{r fastqc, echo=FALSE, eval=T}
fastqc.df=fastqc.table(report.summary$qc.dir)
pander(fastqc.df, justify = "center", style = "multiline", keep.line.breaks = TRUE,split.cells = c("30%","10%","30%","10%","20%"))
```

#### 3-2 FastQC summary
```{r, , echo=FALSE, eval=T, results='asis',fig.keep='all', fig.show=TRUE, fig.height=7, fig.width=7, message=TRUE}

fastqc.summary(fastqc.df, fq1.idx=report.summary$fq1.idx, fq2.idx=report.summary$fq2.idx)
```

File name : Filename provided by user<br />
GC(%) : GC ratio of the total bases<br />
Total reads : Total number of produced reads<br />
Read length(bp) : length of produced reads<br />
Phred Score(>30)(%) : Phred Quality score is a value about probability that a base has been<br />
                      called correctly based on a scale from 10 to 60(Q = -10 log 10 (error rate)).<br />
                      Phred Score(>30)(Q>30) indicates a 99.9% certainty that the base has been called correctly.<br />
                      This is considered high quality data. <br /> 
                      (Q30 = 99.9% certainty (1/1,000 chance of an incorrect base call))<br />


\newpage

```{r per.base.plot, , echo=FALSE, eval=T, warning=FALSE,fig.height=10,fig.width=20,message=FALSE}
fastqc1.idx="_R1_001.fastq"
fastqc2.idx="_R2_001.fastq"
samplename=sub(paste(fastqc1.idx,fastqc2.idx, sep = "|"),"",fastqc.df[,1])
samplename.df=data.frame(Filename=unique(samplename))
qc.figure.path=dir(file.path(report.summary$wd, report.summary$output.name), "per_base_quality.png$", recursive=TRUE, full.names=TRUE)

for(i in 1:(length(unique(samplename))/2)){
  Sample.name=strsplit(samplename, split = "_")[[2*i-1]][1]
  cat(paste0(Sample.name," : Read 1, Read 2"))
  img1<- rasterGrob(as.raster(readPNG(qc.figure.path[2*i-1])),interpolate = FALSE)
  img2<- rasterGrob(as.raster(readPNG(qc.figure.path[2*i])),interpolate = FALSE)
  grid.arrange(img1,img2, ncol=2)
}

```







